draft

### 2020-02-26 src/draft.Rmd
Add files via upload

## R Markdown
```{r}
library(tidyverse)
```

@@

@@

assessment2019<-assessment_pct  %>%  filter(Year=="2019")

data_final<-assessment2017 %>% full_join(assessment2018) %>% full_join(assessment2019)
write.csv(data_final, here("data","data_final.csv"))
```

2. plots

>>>>

## R Markdown
```{r}
library(tidyverse)
library(dplyr)
library(here)
library(readxl)
```

@@

2019 tax pct is missing, we imputed 2019 tax by the average of previous tax pct
```{r}
tax_pct[,4]<-(tax_pct$pct_2017+tax_pct$pct_2018)/2
tax_pct
names(tax_pct)[4]<-paste("pct_2019")
tax_pct
```

@@

assessment2019<-assessment_pct  %>%  filter(Year=="2019")
tax2019<-tax_pct[,c(1,4)]
assessment2019<-assessment2019 %>% left_join(tax2019, by = c("Municipalities"))
names(assessment2019)[9]<-paste("tax")

data_final<-assessment2017 %>% full_join(assessment2018) %>% full_join(assessment2019)
write.csv(data_final, here("data","data_final.csv"))

data_final

```

2. plots
```{r}

```
